Incentivizing Exploration with Unbiased History

### 2018-10-09 algg.tex
update some figures
Hello

\begin{lemma}
\label{lem:greedy}
There exist two constants $\GdT = O_K(1)$ and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least once. 
\end{lemma}

@@

On the other hand, we know that this case happens with probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is at most $2/3$. To sum up, we know that with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once. 
\end{proof}

>>>>

\begin{lemma}
\label{lem:greedy}
There exist two constants $\GdT = O_K(1)$ and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least once. \swcomment{maybe explain what $O_k$ means}
\end{lemma}

@@

In addition, we know that this case happens with probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is at most $2/3$.\swcomment{where did we assume that?} To sum up, we know that with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once. 
\end{proof}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
